---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE 1: This is my personal project to learn how to use Shiny for an interactive dashboard. I am not affiliated with [Reporters Without Borders](https://rsf.org/en) project or website.**     
**NOTE 2: This is work in progress. Just started: About 0% finished**


# rsf

<!-- badges: start -->
<!-- badges: end -->

The goal of `rsf` is to make it easy to compare the World Press Freedom Index as an indicator for the level of freedom enjoyed by journalists and media in 180 countries and territories. 

> “Press freedom is defined as the ability of journalists as individuals and collectives to select, produce, and disseminate news in the public interest independent of political, economic, legal, and social interference and in the absence of threats to their physical and mental safety.

On the basis of this definition, the press freedom questionnaire and map are broken down into five distinct categories or indicators: 

- political context, 
- legal framework, 
- economic context, 
- sociocultural context, and 
- safety

## Installation

You can install the development version of `rsf` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("petzi53/rsf")
```

## Example

This is a basic example which shows you how to start the dashboard:

**Not yet implemented!**

```{r example, eval = FALSE}
library(rsf)

## rsf::run_rsf()
```

